### 2009-02-23 doc/ws-programming-tutorial/doc/tex_echoservice/echoservice.tex
Completed the content of time service (text isnot readable yet) - started content of echo service

\chapter{The echo webservice}

\section{Webservice definition}
wsdl

In case of webservices, which are supported by the KnowArc architecture and used in the present tutorial, the interface of the requests and responses may be definied by a \textit{wsdl} file (WebService Definition Language).

@@

\lstinputlisting
	[
	label=lst:arcecho_arched_xml,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/echoservice/echoservice.cpp}

\lstsetARCHEDXML
\begin{minipage}[t]{\textwidth}
\lstinputlisting
	[
	label=lst:arcecho_arched_xml,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/echoservice/arched_echoservice.xml}
\end{minipage}

\lstsetKSH
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ rm -f /var/log/arched.log
$ arched -c arched_echoservice.xml  && echo jo ||echo n
$ tail -n100 -f /var/log/arched.log
$ killall arched
\end{lstlisting}
\end{minipage}

\lstsetKSH
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ ./echoclient
Tue Feb 17 17:04:08 2009
\end{lstlisting}
\end{minipage}

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:timeservice_cpp_source,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
	<soap-env:Body>
		<echoRequest:echo>
			<echo:say>Der_Berg_ruft</echo:say>
		</echoRequest:echo>
	</soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:timeservice_cpp_source,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <echo:echoResponse>
      <echo:hear>[ Der_Berg_ruft ]</echo:hear>
    </echo:echoResponse>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

>>>>

\chapter{The echo service}

The next service which will be presented is the echo service. It simply returns the received message back to the client.
Depending on the operation requested by the client, the letters of the message will be reordered reverse or not.
The goal of this chapter is to offer a deeper knowledge in message processing. Furthermore the \textit{WSDL} (Web Services Description Language) shall be introduced along with this example.

\section{Web Services Description Language}

Web Services are often reachable for a large set of users in order to easily access complex information. In many cases the Web Service are capable to replace HTML pages i.e. access to databases like Pubmed or the NLM catalog.
% http://www.ncbi.nlm.nih.gov/entrez/query/static/esoap_help.html
In contrary to HTML the interfaces of the data are well defined and easier to find for machines. bla...
Due to that reason, the way to access the web service has to be defined in an own language: \textit{WSDL} (Web Services Description Language).
WSDL is a meta language which determines the structure of the messages along with its permitted elements, the accepted operations, the supported protocols and the address to reach the service. 
The WSDL for the echo service which shall be implemented in this chapter is to be seen in Listing~\ref{lst:echo_wsdl}. There are five main elements to describe a service:
\begin{itemize}
	\item \textbf{Types} --- Definition of the data types used by the messages, line~\ref{lst_code:echo_wsdl_types}.
	\item \textbf{Message} --- Assignments which data types are representing a message, line~\ref{lst_code:echo_wsdl_message1} and \ref{lst_code:echo_wsdl_message2}.
	\item \textbf{Port type} --- \parbox[t]{13cm}{Assignment of the interface: One-way (input), request-response (input, output), solicit-response (input, output, fault), notification (output). The request-response interface is used in line~\ref{lst_code:echo_wsdl_portType}.}
	\item \textbf{Binding} --- Defines the concret protocol and data format used for the message transmission, line~\ref{lst_code:echo_wsdl_binding}.
	\item \textbf{Service} --- Specifies the address to bind a service, line~\ref{lst_code:echo_wsdl_service}.
\end{itemize}
%\textcolor{white}{newline}
\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:echo_wsdl,
	caption={[WSDL file describing the echo service. Filename: echo.wsdl]
	\textbf{HWSDL file describing the echo service. Filename: echo.wsdl}}
	]
{../src/services/echoservice/echo.wsdl}

More information about WSDL may be found at \href{http://www.w3.org/TR/wsdl}{http://www.w3.org/TR/wsdl}.

% a valid service request and the

% WSDL ist eine Metasprache, mit deren Hilfe die angebotenen Funktionen, Daten, Datentypen und Austauschprotokolle eines Web Service beschrieben werden können. Es werden im Wesentlichen die Operationen definiert, die von außen zugänglich sind, sowie die Parameter und Rückgabewerte dieser Operationen. Im Einzelnen beinhaltet ein WSDL-Dokument funktionelle Angaben zu:

%    * der Schnittstelle
%    * Zugangsprotokoll und Details zum Deployment
%    * Alle notwendigen Informationen zum Zugriff auf den Service, in maschinenlesbarem Format

%Nicht enthalten sind hingegen:

%    * Quality-of-Service-Informationen
%    * Taxonomien/Ontologien zur semantischen Einordnung des Services

\section{Service}

The service defined by the WSDL file in the previous section shall now be implemented. The source code of the C++ file is shown in Listing~\ref{lst:echo_service_cpp}. Again the header file will be set aside for it contains to much redundant information.

\lstinputlisting
	[
	label=lst:echo_service_cpp,
	caption={[C++ implementation of the echo service. Filename: echoservice.cpp]
	\textbf{C++ implementation of the echo service. Filename: echoservice.cpp}}
	]
{../src/services/echoservice/echoservice.cpp}

\lstsetARCHEDXML

\lstinputlisting
	[
	label=lst:arcecho_arched_xml, float=htb,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/echoservice/arched_echoservice.xml}

\lstsetKSH
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,float=htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ arched -c arched_echoservice.xml  && echo jo ||echo n
\end{lstlisting}

\section{Client}

@@

\lstsetKSH
\begin{lstlisting}[
label=lst:invokation_arched_timeservice, float=htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ ./echoclient http://localhost:60000/echo ordinary text_to_be_transmitted
[ text_to_be_transmitted ]
$ ./echoclient http://localhost:60000/echo reverse text_to_be_transmitted
[ dettimsnart_eb_ot_txet ]
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:timeservice_cpp_source, float=htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <echo:echoRequest>
      <echo:say operation="reverse">text_to_be_transmitted</echo:say>
    </echo:echoRequest>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:timeservice_cpp_source, float=htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <echo:echoResponse>
      <echo:hear>[ dettimsnart_eb_ot_txet ]</echo:hear>
    </echo:echoResponse>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

### 2009-02-23 doc/ws-programming-tutorial/doc/tex_introduction/introduction.tex
Completed the content of time service (text isnot readable yet) - started content of echo service

\lstinputlisting
	[
	label=lst:arched_arcecho_xml,float,
	caption={[HED configuration. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/arched_arcecho.xml}
The first line of the XML file contains the XML declartion. Several attributes can be defined here but at least the XML version should be specified. \task{What is this ArcConfig for??} % configuration namespaces
The \textit{Server} element, to be found at line~\ref{lst_code:arched_arcecho_Server}, provides basic settings for the daemon such as location of the Pid-file or the Log-file.
The \textit{ModuleManager} holds the path to the plugin libraries. Several paths may be defined here. Due to the fact that the first library fitting to the plugin name is loaded, the order is relevant. The path should be at least assigned to the ARC installation directory. % for the standard MCC are defined here
The next set of elements are holding the name of the plugins to be loaded (line~\ref{lst_code:arched_arcecho_Plugins}).
The names have to correspond to the name of the dynamic libraries within the path defined in the \textit{ModuleManager}.
Finally the chain of the components are declared within the element \textit{Chain}.
Each component inside the chain is represented by an element called \textit{Component} which has at least a name attribute.
Its important that a plugin has been loaded which provides the functionality of it.
Depending on the component certain additional elements may be defined inside of it.
\task{Internet Protocol is required.}
The first component of the chain is the \textit{tcp.service}. As to be seen the port 60000 is assigned to the server to listen to.
The stream which is received by this component is passed to the component defined by the \textit{next} tag.
In the present case it will be passed to the component with the \textit{id} atrribute named \textit{http}. According to this manner the message will be passed to higher layers until it reaches the \textit{Plexer}  Depending on the path of the URL which was demanded by the HTTP the Plexer multiplexes the request to the right Web Service. The path, declared within the \textit{next} element, corresponds to a regular expression and leads to the service with the id named \textit{echo}. 
Hence, the service will now be reachable under URL \textit{http://localhost:60000/echo}.
It will finally process the message and create a new message which will be returned all the way back to the TCP component. The Echo Web Service itself is provided by the ARC package. Additional fix parameters are passed by the elements \textit{prefix} and \textit{suffix}. They set the characters which will enclose the echoed string. %returned 
\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - WEB SERVICE   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - WEB SERVICE}\\

>>>>

\lstinputlisting
	[
	label=lst:arched_arcecho_xml,float,
	caption={[HED configuration. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/arched_arcecho.xml}
The first line of the XML file contains the XML declartion. Several attributes can be defined here but at least the XML version should be specified. \task{What is this ArcConfig for??} % configuration namespaces
The \textit{Server} element, to be found at line~\ref{lst_code:arched_arcecho_Server}, provides basic settings for the daemon such as location of the Pid-file or the Log-file.
The \textit{ModuleManager} holds the path to the plugin libraries. Several paths may be defined here. Due to the fact that the first library fitting to the plugin name is loaded, the order is relevant. The path should be at least assigned to the ARC installation directory. % for the standard MCC are defined here
The next set of elements are holding the name of the plugins to be loaded (line~\ref{lst_code:arched_arcecho_Plugins}).
The names have to correspond to the name of the dynamic libraries within the path defined in the \textit{ModuleManager}.
Finally the chain of the components are declared within the element \textit{Chain}.
Each component inside the chain is represented by an element called \textit{Component} which has at least a name attribute.
Its important that a plugin has been loaded which provides the functionality of it.
Depending on the component certain additional elements may be defined inside of it.
\task{Internet Protocol is required.}
The first component of the chain is the \textit{tcp.service}. As to be seen the port 60000 is assigned to the server to listen to.
The stream which is received by this component is passed to the component defined by the \textit{next} tag.
In the present case it will be passed to the component with the \textit{id} atrribute named \textit{http}. According to this manner the message will be passed to higher layers until it reaches the \textit{Plexer}  Depending on the path of the URL which was demanded by the HTTP the Plexer multiplexes the request to the right Web Service. The path, declared within the \textit{next} element, corresponds to a regular expression and leads to the service with the id named \textit{echo}. 
Hence, the service will now be reachable under URL \textit{http://localhost:60000/echo}.
It will finally process the message and create a new message which will be returned all the way back to the TCP component. The Echo Web Service itself is provided by the ARC package. Additional fix parameters are passed by the elements \textit{prefix} and \textit{suffix}. They set the characters which will enclose the echoed string. %returned 
\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - WEB SERVICE   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - WEB SERVICE}\task{remark in \textbf{introduction}, what the plexer is for. In our case: to have several services running on one port!!!!!!!!}\\

### 2009-02-23 doc/ws-programming-tutorial/doc/tex_timeservice/timeservice.tex
Completed the content of time service (text isnot readable yet) - started content of echo service

In Arc the services are implementated as plugins such that they can easily be included or excluded by modifiying the HED configuration file as it was to be seen in Listing~\ref{lst:arched_arcecho_xml}.
Listing~\ref{lst:time_arched_cpp} contains the C++ implementation of the time service plugin.
The proper class definition of the object \textit{TimeService} is defined in the corresponding header file which is not shown here. It inherits from an object called \textit{Service} defined in the Arc library.
The key element for each plugin is the struct \textit{PluginDescriptor} named \textit{PLUGINS\_TABLE\_NAME} to be seen in line~\ref{lst_code:time_cpp_ptn}. 
%The struct defines basic entities of the service and provides a pointer to the method which is able to create an instance of the time service plugin.
Within the struct a unique plugin name, the type of the plugin, its version and a pointer to a function which returns the instance of the time service has to be defined.
The function which returns the pointer of the instance is desclared in line~\ref{lst_code:time_cpp_get_service}. 
The interface demands an object \textit{PluginArgument} as a parameter but because we are writing a plugin which inherits from \textit{Service}, we are able to expect the \textit{PluginArgument} to be a \textit{ServicePluginArgument}.
%	In the first line of the service the object is downcasted with the operator dynamic_cast
The \textit{ServicePluginArgument} provides access to the HED configuration and the message chain of the service.
%       operator Config* (void) { return config_; };
%       operator ChainContext*   			an interface to manipulate chains stored in Loader
%
%
%
%
The time service uses the namespace \textit{ArcService}. The constructor can be found in line~\ref{lst_code:time_cpp_constructor} and the deconstructor in line~\ref{lst_code:time_cpp_deconstructor}.%
\lstsetCPP%
\lstinputlisting[
	label=lst:time_arched_cpp,
	caption={[C++ implementation of the time service. Filename: timeservice.cpp]
	\textbf{C++ implementation of the time service. Filename: timeservice.cpp}}
	]%
{../src/services/timeservice/timeservice.cpp}%
In the context of the simple service they don't contribute with any functionality.
The method \textit{process} which is required by the inherited class \textit{Service} is defined in line~\ref{lst_code:time_cpp_process} and realises the desired service. 
The parameters \textit{inmsg} and \textit{outmsg} are references to the incoming and outgoing messages. Furthermore the method \textit{process} returns the object \textit{MCCStatus} which is representing the result of the service achieved. 
Within the method \textit{process}, the service first determines the current time and than creates a SOAP payload using the object \textit{PayloadSOAP} on line~\ref{lst_code:time_cpp_process_payloadSOAP}. 
The object \textit{PayloadSOAP} provides enough functionality to create a XML message which is conform to the SOAP protocol 
(The apperance of the generated request and response will be discussed later on page~\pageref{lst:time_client_request}). 
%
%
In the current case the payload consists of two elements nested into one another. The element \textit{time} holds the element \textit{timeResponse} which again holds the string containing the current time.
Within the line~\ref{lst_code:time_cpp_process_message_payload} the payload is stored in the message. 
In case nothing unexpected happened during the message is processed, the function returns with an \textit{MCCStatus} set to \textit{OK} as to be seen in line~\ref{lst_code:time_cpp_return}.\\

@@

%\task{\#ifdef HAVE\_CONFIG\_H\#include <config.h>\#endif - habe ich entfernt... macht keinen Sinn, da keine weiteren Macros im Source Code enthalten sind... oder?}
In the next step a simple client needs to be implemented whose task is to interprete the returned message of the client.
The client needs to have the same protocol stack as the daemon but in contrast to it, it does not need the ability to be loaded as a plugin. As one will see, the creation of this protocol stack on client side is very simple.
The source code of the client consists primarily of the main function and is to be seen in Listing~\ref{lst:time_client_cpp}.
In line~\ref{lst_code:time_client_cpp_logger} the logger is initialized and redirected to the standard error stream.
For the components of the protocol stack are likewise loaded dynamically, one need to specify the installation directory in line~\ref{lst_code:time_client_cpp_init} too.
\task{remark in \textbf{introduction}, what the plexer is for. In our case: to have several services running on one port!!!!!!!!}
The URL of the service is defined in line~\ref{lst_code:time_client_cpp_url}. It fits to the HED configuration file which was shown in Listing~\ref{lst:time_arched_xml}. The daemon is listing on port 60000 and is running on the localhost. The service itself uses HTTP and can be reached by using the path \textit{time}.
Line~\ref{lst_code:time_client_cpp_config} loads the standard config file which is usually almost empty. As a result, no additional security procedures will later be linked into the client sided stack. The protocol stack is created in line~\ref{lst_code:time_client_cpp_client}. Thanks to the URL the information for the configuration can be completed.
The constructor of the class \textit{ClientSOAP} creates a SOAP client which uses HTTP, addresses the port 60000 on localhost. If i.e. HTTPS would have been used, the stack would have been extended by a TLS layer.
Now the client stack is ready, one can create a request to the service. In line~\ref{lst_code:time_client_cpp_message_reqeust} a message which corresponds to the Listing~\ref{lst:time_client_request} is created. The message gets processed by the command in line~\ref{lst_code:time_client_cpp_message_response}. If everything was fine, the message will finally be send to the standard out in line~\ref{lst_code:time_client_cpp_message_answer}.

\lstsetCPP
\lstinputlisting
	[
	label=lst:time_client_cpp,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/timeclient/timeclient.cpp}

Once the HED is running, the service can

The data is enveloped by an element called \textit{Envelope} .. See german wiki

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:time_client_request,float,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:time="urn:time" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeRequest></timeRequest>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:time_client_response,float,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeResponse>Wed Feb 18 11:20:30 2009</timeResponse>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

\lstsetKSH
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=st:time_client_ksh,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ ./timeclient
Wed Feb 18 11:20:30 2009
\end{lstlisting}
\end{minipage}

>>>>

In Arc the services are implementated as plugins such that they can easily be included or excluded by modifiying the HED configuration file as it was to be seen in Listing~\ref{lst:arched_arcecho_xml}.
Listing~\ref{lst:time_arched_cpp} contains the C++ implementation of the time service plugin.
The proper class definition of the object \textit{TimeService} is defined in the corresponding header file which is not shown here. It inherits from an object called \textit{Service} defined in the Arc library.
The key element for each plugin is the struct \textit{PluginDescriptor} named \textit{PLUGINS\_TABLE\_NAME} to be seen in line~\ref{lst_code:time_cpp_ptn}. 
%The struct defines basic entities of the service and provides a pointer to the method which is able to create an instance of the time service plugin.
Within the struct a unique plugin name, the type of the plugin, its version and a pointer to a function which returns the instance of the time service has to be defined.
The function which returns the pointer of the instance is desclared in line~\ref{lst_code:time_cpp_get_service}. 
The interface demands an object \textit{PluginArgument} as a parameter but because we are writing a plugin which inherits from \textit{Service}, we are able to expect the \textit{PluginArgument} to be a \textit{ServicePluginArgument}.
%	In the first line of the service the object is downcasted with the operator dynamic_cast
The \textit{ServicePluginArgument} provides access to the HED 
%       operator Config* (void) { return config_; };
%       operator ChainContext*   			an interface to manipulate chains stored in Loader
%
%
%
%
 \textcolor{white}{newline}
\lstsetCPP%
\lstinputlisting[
	label=lst:time_arched_cpp,
	caption={[C++ implementation of the time service. Filename: timeservice.cpp]
	\textbf{C++ implementation of the time service. Filename: timeservice.cpp}}
	]%
{../src/services/timeservice/timeservice.cpp}%
configuration and the message chain of the service. The time service uses the namespace \textit{ArcService}. The constructor can be found in line~\ref{lst_code:time_cpp_constructor} and the deconstructor in line~\ref{lst_code:time_cpp_deconstructor}. In the context of the simple service they don't contribute with any functionality. Only the constructor is defining the XML null-namespace for the time service.
The method \textit{process} which is required by the inherited class \textit{Service} is defined in line~\ref{lst_code:time_cpp_process} and realises the desired service. 
The parameters \textit{inmsg} and \textit{outmsg} are references to the incoming and outgoing messages. Furthermore the method \textit{process} returns the object \textit{MCCStatus} which is representing the result of the service achieved. 
Within the method \textit{process}, the service first determines the current time and than creates a SOAP payload using the object \textit{PayloadSOAP} on line~\ref{lst_code:time_cpp_process_payloadSOAP}. 
The object \textit{PayloadSOAP} provides enough functionality to create a XML message which is conform to the SOAP protocol 
(The apperance of the generated request and response will be discussed later on page~\pageref{lst:time_client_request}). 
%
%
In the current case the payload consists of two elements nested into one another. The element \textit{time} holds the element \textit{timeResponse} which again holds the string containing the current time.
Within the line~\ref{lst_code:time_cpp_process_message_payload} the payload is stored in the message. 
In case nothing unexpected happened during the message is processed, the function returns with an \textit{MCCStatus} set to \textit{OK} as to be seen in line~\ref{lst_code:time_cpp_return}.\\

@@

%\task{\#ifdef HAVE\_CONFIG\_H\#include <config.h>\#endif - habe ich entfernt... macht keinen Sinn, da keine weiteren Macros im Source Code enthalten sind... oder?}
This section is introducing the implementation of the client whose main task is to interprete the returned message.
In order to be able to communicate with the service providing daemon the client needs to use an identic protocol stack.
Likewise to the HED it will also be created dynamically using the MCCs.
But as one will see, the creation of the protocol stack on client side is very simple.
%
%
%
The source code of the client is to be seen in Listing~\ref{lst:time_client_cpp} and consists basically of one main function. Within the line~\ref{lst_code:time_client_cpp_logger} the object \textit{Logger} gets initialized. Due to the configuration of the the \textit{Logger} in the next lines, the messages passed to it will be redirected to the standard error stream.
%
For the components of the protocol stack are likewise loaded \textcolor{white}{newline}
\lstsetCPP
\lstinputlisting
	[
	label=lst:time_client_cpp,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/timeclient/timeclient.cpp}
 dynamically, one need to specify the installation directory of ARC in line~\ref{lst_code:time_client_cpp_init}.
%
The URL of the service is defined in line~\ref{lst_code:time_client_cpp_url}. It fits to the HED configuration file which was shown in Listing~\ref{lst:time_arched_xml}. 
The daemon is listing on port 60000 and is running on the localhost. The service itself uses HTTP and can be reached by using the path \textit{time}.
Line~\ref{lst_code:time_client_cpp_config} loads the standard config file which is usually almost empty. As a result, no additional security procedures will later be linked into the client sided stack. 
The protocol stack is created in line~\ref{lst_code:time_client_cpp_client}. 
Thanks to the service URL the information for the configuration is complete.
The constructor of the class \textit{ClientSOAP} creates a SOAP client which uses HTTP and addresses the port 60000 on localhost. If i.e. HTTPS would have been used, the stack would have been extended by an additional TLS protocol.
Once the client stack is ready, the request to the service can be created which is done in line~\ref{lst_code:time_client_cpp_message_reqeust}. Even the apperance of the message is unimportant to the service, the message is composed of two convoluted elements \textit{time} and \textit{timeReqest}.
%
The request will be processed in the next line by the method \textit{process} of the object \textit{client}.%in line~\ref{lst_code:time_client_cpp_message_response}. 
The object \textit{MCCStatus} which is returned by the method indicates the success of the processing.
After verifying the response, the message will passed to the standard out in line~\ref{lst_code:time_client_cpp_message_answer}.\\

The client has to be compilied to an ordinary binary so it can directly be executed from the command line.
Assure the service is running and use the client as to be seen in Listing~\ref{lst:time_client_ksh}.
\lstsetKSH
\begin{lstlisting}[
label=lst:time_client_ksh,float=htb,
caption={[Invokation of the time client.]
         \textbf{Invokation of the time client}}]
$ ./timeclient
Wed Feb 18 11:20:30 2009
\end{lstlisting}
The structure of the messages on SOAP level which are transmitted are shown in the Listings~\ref{lst:time_client_request} and \ref{lst:time_client_response}.
The enclosing element is \textit{Envelope} which may contain an element \textit{Header} and must contain an element \textit{Body}. %The namespace \textit{soap-env} is defined by the element \textit{envelope}
The data created by the object \textit{PayloadSOAP} is to be found within the \textit{Body}.
\lstsetJUSTXML
\begin{lstlisting}[
label=lst:time_client_request,float=htb,
caption={[Request message created by the client.]
         \textbf{Request message created by the client}}]
<soap-env:Envelope xmlns="urn:time" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeRequest></timeRequest>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:time_client_response,float=htb,
caption={[Responce message of the service.]
         \textbf{Responce message of the service}}]
<soap-env:Envelope xmlns="urn:time" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeResponse>Wed Feb 18 11:20:30 2009</timeResponse>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
